Comparing corrosion control treatments for drinking water using a robust Bayesian generalized additive model

### 2022-07-18 Rmarkdown/paper.Rmd
edit fig 6, add SI description, keywords

@@

Supplementary information for this article includes additional description of the pipe loop study, a comparison of different prior choices, models summaries, and convergence statistics.

@@

>>>>

## Keywords

GAM; time series analysis; censored data; pipe loop; Lead and Copper Rule

@@

## Supporting information

The Supporting Information is available free of charge via the internet at http://pubs.acs.org.

Additional description of the pipe loop study and the statistical model, including model summaries, convergence statistics, and a comparison of different prior choices.

@@

<div id="refs"></div>

# TOC graphic
